Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2019-08-23 resistingrhythm/analysis/paper_figures_v4.Rmd
Add FI figure to Rmd

# Figure: Theta results
```{r fig.height=2.25, fig.width=6}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="b.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

@@

```{r}
print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
```

@@

layout_matrix <- rbind(
  c(1, 1, 1, 1, 3),
  c(2, 2, 2, 2, 3)
)
grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
```

@@

png(file="fig4.png", bg="white", width=4.8, height=5.6, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
dev.off()
```

>>>>

## FI curve
```{r, message=FALSE}
results_fi <- read_csv("../ipynb/FI_curves.csv")
```
# Figure: Theta results
```{r fig.height=2.25, fig.width=6}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="b.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

@@

```{r}
print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
```
# Figure: FI 
```{r, fig.height=0.9, fig.width=1.9}
win <- 50e-3
N <- 100
us <- 1e6
results_fi %>% 
ggplot() +
  geom_line(aes(x=impulse*us, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
  geom_line(aes(x=impulse*us, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
  labs(tag="a.", y="Avg. rate", x=TeX("Impulse ($\\mu$siemens)")) +
  lims(x=c(0, 10)) +
  scale_colour_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    plot.tag = element_text(size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm")
  ) -> p1
print(p1)

png(file="fig3.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
print(p1)
dev.off()
```

@@

layout_matrix <- rbind(
  c(1, 1, 1, 1, 3),
  c(2, 2, 2, 2, 3)
)
grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)

png(file="fig4.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
dev.off()
```

@@

png(file="fig5.png", bg="white", width=10, height=7.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)
dev.off()
```
